A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
Finished section 5.2. Now Haoyu and I will finish Section 5.3

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp2.png}
    \caption{Experiment results of Logistic regression}
    \label{fig:logistic_fig}
    %\vspace{-10pt}
\end{figure}

We use this experiment to illustrate another property of our minibatch MH testing: when the size of
minibatch increase to a threshold, the accuracy / log likelihood of sampled data at a fix iteration
number will not improve with larger minibatch size, see Fig.~4c. This is because the variance of
$\Delta'$ decrease with large minibatch, and the error of our minibatch MH testing is proportional
to our estimation error of variance of $\Delta'$. When the ${\rm Var}(\Delta')$ decrease to a
threshold, the error of our minibatch MH testing can be ignored.

@@

\begin{figure}[t]
    \centering
    \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
    %\includegraphics[width=0.5\linewidth]{empty}
    \caption{This will hopefully show results for neural networks on BIDMach.}
    \label{fig:nnet_fig}
    %\vspace{-10pt}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp2.png}
    \caption{Logistic regression performance (accuracy/log likelihood) and minibatch size analysis.}
    \label{fig:logistic_fig}
    %\vspace{-10pt}
\end{figure}

The third plot of Figure~\ref{fig:logistic_fig} shows performance based on minibatch size, when the
performance is evaluated on the test set after training iterations 700, 1000, and 1500. For all
three iteration counts, when the minibatch size increases beyond about 10, the performance of the
sampled data will not improve with a large minibatch size. This makes sense because the error of our
MH test is proportional to our estimation error of ${\rm std}(\Delta')$, and as the minibatch
increases, ${\rm std}(\Delta')$ decreases. Beyond a certain standard deviation threshold, the error
in our minibatch MH test is negligible.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp3}
    \caption{TODO This will hopefully show results for neural networks on BIDMach.}
    \label{fig:nnet_fig}
    %\vspace{-10pt}
\end{figure}
